Optimal (Multiway) Spatial Joins

### 2024-05-23 msj.tex
yufei

    \item $v_1$ (resp., $v_2$): the leftmost (resp., rightmost) segment --- i.e., with the smallest (resp., largest) x-coordinate --- among all the segments in $V$ that cross $r$.
}
Define $r_1'$ as the rectangle defined by the above four segments in the way shown in Figure~\ref{fig:hv:type1}(a) ($r_1'$ is the shaded area). Note that $r_1'$ exists if and only if $r_1$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$. Moreover, it is possible for $h_1$ and $h_2$ to be the same segment; same for $v_1$ and $v_2$. Define
\myeqn{
    R_1' &=& \set{r_1' \mid r_1 \in R_1 \text{ and its $r_1'$ defined as above exists}}. \nn
}
Computing the corresponding ``segment $h_1$'' for each $r_1 \in R_1$ is an instance of Problem $\EuScript{A}$. By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r_1 \in R_1$. It thus follows from Section~\ref{sec:bricks} that $R_1'$ can be produced in $O(n \log n)$ time and $O(n)$ space.

@@

The proof is presented in Appendix~\ref{app:lmm:hv:type1:proj}. Note that the size of $\Pi_{1:k-2}(\J_1(R_1, ...,$ $R_{k-2}, H, V))$ is bounded by that of $\J_1(R_1, ..., R_{k-2},$ $H, V)$, which in turn is bounded by $\out$. Thus, as a corollary of Lemma~\ref{lmm:hv:type1:proj}, the $(k-2)$-SJ instance $R_1', R_2, ..., R_{k-2}$  can be settled in $F_{k-2}(n, \out)$ time using $G_{k-2}(n, \out)$ space.

\extraspacing {\bf Step 2.} We are ready to explain how to produce $\J_1(R_1, ..., R_{k-2}, H, V)$ from $\Pi_{1:k-2}(\J_1(R_1, ...,$ $R_{k-2}, H, V))$. Our algorithm for this purpose will find a set $S$ satisfying
\myeqn{
    \J_1(R_1, ..., R_{k-2}, H, V) 
    \subseteq 
    S
    \subseteq 
    \J(R_1, ..., R_{k-2}, H, V). \label{eqn:hv:type1:S}
}
Recall that $\J(R_1, ..., R_{k-2}, H, V)$ is the result of the original H-V $k$-SJ problem, which has a size of $\out$. Only the $k$-tuples in $S$ that are of Type 1 will be reported. We will achieve the purpose in time $O(n \log n + |S|)$ and space $O(n + |S|)$.

@@

\noindent In Appendix~\ref{app:hv:type1:gen-S}, we prove that the set $S$ computed satisfies \eqref{eqn:hv:type1:S}, as desired. The running time of the above algorithm is
\myeqn{
    O(1 + |\Pi_{1:k-2}(\J_1(R_1, ..., R_{k-2}, H, V))| + |S|) = O(1 + \out) \nn
}
and its space is bounded by $O(\out)$.

>>>>

    \item $v_1$ (resp., $v_2$): the leftmost (resp., rightmost) segment --- i.e., with the smallest (resp., largest) x-coordinate --- among all the segments in $V$ that cross $r$.
}
Define $r_1'$ as the rectangle defined by the above four segments in the way shown in Figure~\ref{fig:hv:type1}(a) ($r_1'$ is the shaded area). Note that $r_1'$ exists if and only if $r_1$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$. Moreover, it is possible for $h_1$ and $h_2$ to be the same segment; same for $v_1$ and $v_2$. Define
\myeqn{
    R_1' &=& \set{r_1' \mid r_1 \in R_1 \text{ and its $r_1'$ defined as above exists}}. \nn
}
Computing the corresponding ``segment $h_1$'' for each $r_1 \in R_1$ is an instance of Problem $\EuScript{A}$. By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r_1 \in R_1$. It thus follows from Section~\ref{sec:bricks} that $R_1'$ can be produced in $O(n \log n)$ time.

@@

The proof is presented in Appendix~\ref{app:lmm:hv:type1:proj}. Note that the size of $\Pi_{1:k-2}(\J_1(R_1, ...,$ $R_{k-2}, H, V))$ is bounded by that of $\J_1(R_1, ..., R_{k-2},$ $H, V)$, which in turn is bounded by $\out$. Thus, as a corollary of Lemma~\ref{lmm:hv:type1:proj}, the $(k-2)$-SJ instance $R_1', R_2, ..., R_{k-2}$  can be settled in $F_{k-2}(n, \out)$ time.

\extraspacing {\bf Step 2.} We are ready to explain how to produce $\J_1(R_1, ..., R_{k-2}, H, V)$ from $\Pi_{1:k-2}(\J_1(R_1, ...,$ $R_{k-2}, H, V))$. Our algorithm for this purpose will find a set $S$ satisfying
\myeqn{
    \J_1(R_1, ..., R_{k-2}, H, V) 
    \subseteq 
    S
    \subseteq 
    \J(R_1, ..., R_{k-2}, H, V). \label{eqn:hv:type1:S}
}
Recall that $\J(R_1, ..., R_{k-2}, H, V)$ is the result of the original H-V $k$-SJ problem, which has a size of $\out$. Only the $k$-tuples in $S$ that are of Type 1 will be reported. We will achieve the purpose in $O(n \log n + |S|)$ time.

@@

\noindent In Appendix~\ref{app:hv:type1:gen-S}, we prove that the set $S$ computed satisfies \eqref{eqn:hv:type1:S}, as desired. If we exclude the time to compute all the $\cross(r_a, B; H)$ and $\cross(r_b, B; V)$, the running time of the above algorithm is
\myeqn{
    O(1 + |\Pi_{1:k-2}(\J_1(R_1, ..., R_{k-2}, H, V))| + |S|) \nn
}
which is $O(1 + \out)$ because of \eqref{eqn:hv:type1:S}. In what follows, we will explain how to compute all the $\cross(r_a, B; H)$ in $O(n \log n + |S|)$ time. A symmetric algorithm can be used to compute
